%         ░█▄▒▄█▒██▀░█▀▄░░░▄▀▀░█▒█░░░▀█▀▒██▀░█▄▒▄█▒█▀▄░█▒░▒▄▀▄░▀█▀▒██▀
%         ░█▒▀▒█░█▄▄▒█▄▀▒░░▀▄▄░▀▄▀▒░░▒█▒░█▄▄░█▒▀▒█░█▀▒▒█▄▄░█▀█░▒█▒░█▄▄
%
%
%   This is a LaTex/Bibtex template for academic medicine.
%   Details at https://github.com/alexgoodell/academic-medicine-cv

%   Inspired by the following repos. Drop a star if helpful to you!
%         - https://github.com/Xovee/latex-cv
%         - https://github.com/rgeirhos/academic-cv-publications


% ███████████████████████████████ PREAMBLE █████████████████████████████████████


% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ IMPORT ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

% \documentclass[10pt]{article}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[full]{textcomp}
\usepackage{CJKutf8}
\usepackage[lf]{ebgaramond}
%\usepackage[scaled,swashQ]{garamondx}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{eqparbox}


% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ PAGE SETUP ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{headings}
%\markright{\textit{John E. Smith}} %header off
\setlength\parindent{2em}
\thispagestyle{empty}


% ━━━━━━━━━━━━━━━━━━━━━ CUSTOM HEADERS AND LISTS ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

% cv sections
\newcommand{\cvsection}[1]{\section*{\rmfamily#1}}
\newcommand{\cvsubsection}[1]{\subsection*{\rmfamily\hspace{1.5em}#1}}
\newcommand{\cvsubsubsection}[1]{\subsubsection*{\rmfamily\hspace{1em}#1}}
\newcommand{\HL}[1]{\textbf{\color{red}#1}}

% my list
\usepackage{enumitem}
\usepackage{mweights}
\newcommand{\myliststart}{\begin{description}[font=\normalfont,
    labelindent=2em,leftmargin=10em,style=nextline]}
\newcommand{\mylistend}{\end{description}}

% presentation list
\newcommand{\presentationliststart}{\begin{description}[font=\normalfont,
    labelindent=2em,leftmargin=7em,style=nextline]}
\newcommand{\presentationlistend}{\end{description}}




% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ CITATIONS ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

% Import reference manager
\usepackage{babel}
\usepackage[
  backend=biber,
  % style=reading,
  style=nature,
  intitle = true, % allows for chapter title inclusion
  isbn=true,
  doi=true,
  url=true,
  sorting=ynt,
  clearlang=true,
  date=year,
  uniquelist=false,
  maxbibnames=12,
  maxcitenames=1,
  defernumbers=true
]{biblatex}

% define bibliograph source
\addbibresource{bibliography.bib}

% Add unique entry type for dataset
\DefineBibliographyStrings{english}{
  dataset = {dataset},
}
\renewbibmacro{begentry}{%
  \ifkeyword{meta}{\textsuperscript{*}}{}%
  \ifentrytype{dataset}
    {\bibstring{[dataset] }%
     \setunit{\addspace}}
    {}%
}

% remove "et al" styling
\renewbibmacro*{name:andothers}{%
  \ifboolexpr
    {
      test {\ifnumequal{\value{listcount}}{\value{liststop}}}
      and
      test \ifmorenames
    }
  {
        \ifnumgreater{\value{liststop}}{1}
      {\finalandcomma}
      {}%
      \andothersdelim
      \bibstring{andothers}%
    }
  {}%
}

% add a left indent on bibliography
\defbibenvironment{bibliography}
  {\list
     {\printtext[labelnumberwidth]{%
      \printfield{labelprefix}%
      \printfield{labelnumber}}}
     {\setlength{\labelwidth}{\labelnumberwidth}%
      \setlength{\leftmargin}{\labelwidth}%
      \setlength{\labelsep}{\biblabelsep}%
      \addtolength{\leftmargin}{\labelsep}%
      \addtolength{\leftmargin}{2em}%<----- here
      \setlength{\itemsep}{\bibitemsep}%
      \setlength{\parsep}{\bibparsep}}%
      \renewcommand*{\makelabel}[1]{\hss##1}}
  {\endlist}
  {\item}

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ LINKS ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\usepackage[
    hidelinks,
    pdfnewwindow=true,
    pdfauthor={John E. Smith},
    pdftitle={Curriculum Vitae of John E. Smith},
    pdfpagemode=UseThumbs,
]{hyperref}
\hypersetup{colorlinks=true, linkcolor=teal, urlcolor=teal, citecolor=teal, anchorcolor=teal}
\usepackage{xurl}


% ███████████████████████████████ DOCUMENT █████████████████████████████████████


\begin{document}

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ Title Content ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

% name
\begin{center}
    \Huge{\textbf{Curriculum Vitae}}
\end{center}

\begin{center}
    \large{\textit{John E. Smith, MD}}
\end{center}

\vspace{15pt}


\setlength{\parskip}{5pt}
\renewcommand{\arraystretch}{1.25}

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━ Identifying data ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{A. Identifying Data}


\myliststart
\item[Name] John Edward Smith
\item[Website] \url{https://johnsmith.com}
\mylistend

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━ Academic History ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{B. Academic History}

\cvsubsection{Colleges and Universities Attended:}
\indent

\eqparbox[t]{date}{9/2005 \textendash~5/2009} \hfill
\eqparbox{degree}{B.S.} \hfill
\eqparbox{major}{Biochemistry} \hfill
\eqparbox{edu-univ}{Ivy League University} \hfill


\eqparbox[t]{date}{8/2009 \textendash~5/2011} \hfill
\eqparbox{degree}{M.S.} \hfill
\eqparbox{major}{Molecular Biology} \hfill
\eqparbox{edu-univ}{State University} \hfill

\eqparbox[t]{date}{8/2011 \textendash~5/2015} \hfill
\eqparbox{degree}{M.D.} \hfill
\eqparbox{major}{Medicine} \hfill
\eqparbox{edu-univ}{Top Medical School} \hfill

\cvsubsection{Post-graduate Training:}
\indent

\myliststart
\item[6/2015 \textendash~6/2018] Residency in Internal Medicine, University Hospital
\item[7/2018 \textendash~6/2021] Fellowship in Cardiology, Academic Medical Center
\item[7/2021 \textendash~6/2022] Advanced Fellowship in Interventional Cardiology, Research Institute
\mylistend

\cvsubsection{Board Certification:}
\myliststart
\item[10/2018] American Board of Internal Medicine
\item[11/2021] American Board of Cardiovascular Disease
\mylistend

\cvsubsection{Licensure:}
\myliststart
\item[7/2015] Physician and Surgeon, State Medical Board
\mylistend


% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ Employment ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{C. Employment}

\cvsubsection{Academic Appointments:}

\myliststart
\item[7/2022 \textendash~Present] Assistant Professor, Department of Medicine, Division of Cardiology, University Medical Center
\item[8/2022 \textendash~Present] Attending Physician, Cardiac Catheterization Laboratory, University Hospital
\mylistend

\cvsubsection{Other Appointments:}

\myliststart
\item[6/2008]	Research Assistant, Cardiovascular Research Lab, Ivy League University
\item[6/2010 \textendash~8/2010]	Clinical Research Intern, National Heart Institute
\item[7/2013]	Medical Student Researcher, Global Health Initiative, Top Medical School
\item[9/2016 \textendash~6/2018]	Quality Improvement Fellow, Department of Medicine, University Hospital
\mylistend


% ━━━━━━━━━━━━━━━━━━━━━ Teaching and Clinical Care ━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{D. Teaching and Clinical Care}

\cvsubsubsection{Clinical Teaching Responsibilities:}

\myliststart
\item[9/2022 \textendash~Present] Course Director, Cardiovascular Physical Examination, Medical Student Education, University Medical Center
\item[7/2023 \textendash~Present] Faculty Mentor, Cardiology Fellowship Program, University Medical Center
\mylistend


\cvsubsubsection{Students / Trainees / Mentorship:}
\myliststart
\item[6/2023 \textendash~Present]	Jane Doe, MD/PhD Student, School of Medicine, University Medical Center, 2 hours / week
Advising thesis project on novel biomarkers for early detection of heart failure.
\item[9/2023 \textendash~Present]	Richard Roe, Cardiology Fellow, Department of Medicine, University Medical Center, 1 hour / week
Mentoring research project on outcomes of transcatheter aortic valve replacement in octogenarians.
\mylistend

% ━━━━━━━━━━━━━━━━━━━━━ Public and Professional Service ━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{E. Public and Professional Service}

\cvsubsection{Community Service Related to Professional Work:}

\myliststart
\item[6/2016 \textendash~Present] Volunteer Physician, Free Medical Clinic, Local Community Health Center
\item[9/2019 \textendash~Present]	Medical Advisory Board Member, Heart Health Foundation
\item[3/2021 \textendash~Present]	Scientific Committee Member, National Cardiovascular Disease Prevention Initiative
\mylistend

\cvsubsection{Professional Societies:}

\myliststart
\item[2015]	Member, American College of Physicians
\item[2018]	Member, American Heart Association
\item[2021]	Fellow, American College of Cardiology
\item[2022]	Member, Society for Cardiovascular Angiography and Interventions
\mylistend

\cvsubsection{Ad Hoc Reviewer:}

\myliststart
\item[2020]	Journal of the American College of Cardiology
\item[2021]	Circulation
\item[2022]	New England Journal of Medicine
\mylistend

% ━━━━━━━━━━━━━━━━━━━━━ Honors and Awards  ━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{F. Post-Degree Honors and Awards}

\myliststart

\item[5/2015]   Alpha Omega Alpha Honor Medical Society, Top Medical School
\item[6/2018]   Resident Teacher of the Year Award, Department of Medicine, University Hospital
\item[11/2020]  Young Investigator Award, American Heart Association Scientific Sessions
\item[9/2021]   Excellence in Research Award, Cardiology Fellowship Program, Academic Medical Center
\item[3/2023]   Early Career Investigator Grant, National Heart, Lung, and Blood Institute
\item[6/2024]   Outstanding Junior Faculty Award, Department of Medicine, University Medical Center

\mylistend

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ Bibliography ━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{G. Bibliography}

\nocite{*} % required for fake cite everything

\cvsubsection{Peer-reviewed articles}
    \indent \printbibliography[keyword={published article},heading=none,resetnumbers=true]

\cvsubsection{Peer-reviewed articles, submitted}
    \printbibliography[keyword={submitted article},heading=none,resetnumbers=true]

\cvsubsection{Peer-reviewed abstracts}
    \printbibliography[keyword={abstract},heading=none,resetnumbers=true]

\cvsubsection{Book chapters}
    \printbibliography[keyword={chapter},heading=none,resetnumbers=true]

\cvsubsection{Books}
    \printbibliography[keyword={book},heading=none,resetnumbers=true]

\cvsubsection{Digital publications and datasets}
    \printbibliography[keyword={dataset},heading=none,resetnumbers=true]

\cvsubsection{Other publications}
    \printbibliography[keyword={photography},heading=none,resetnumbers=true]

% ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━ Presentations ━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━

\cvsection{H. Invited Presentations}

\cvsubsection{Local presentations}

\presentationliststart
    \item[9/2018] \textbf{Smith, J. E.}. Advances in Cardiovascular Risk Assessment. Grand Rounds, Department of
    Medicine, University Hospital.
    \item[3/2019] \textbf{Smith, J. E.}, Johnson, A. B. Novel Biomarkers in Acute Coronary Syndrome.
    Cardiology Fellowship Lecture Series, Academic Medical Center.
    \item[11/2020] \textbf{Smith, J. E.} Optimizing Door-to-Balloon Time in ST-Elevation Myocardial Infarction.
    Quality Improvement Seminar, University Hospital.
    \item[5/2021] \textbf{Smith, J. E.} The Role of Cardiac MRI in Diagnosing Myocarditis.
    Radiology-Cardiology Joint Conference, University Medical Center.
    \item[2/2022] \textbf{Smith, J. E.} Transcatheter Aortic Valve Replacement: Current Evidence and Future Directions.
    Cardiovascular Medicine Update, State Medical Society.
    \item[10/2023] \textbf{Smith, J. E.}, Davis, C. D. Artificial Intelligence in Cardiovascular Imaging: Promises and Pitfalls.
    Medical Informatics Symposium, University Medical Center.
    \url{https://medcenter.edu/ai-cardio-imaging}
\presentationlistend

\cvsubsection{National presentations:}

\presentationliststart
    \item[11/2019] Smith, J.E., Johnson, A.B., Brown, M.L. Long-term Outcomes of Early Invasive Strategy in Non-ST Elevation Myocardial Infarction.
    American Heart Association Scientific Sessions, Philadelphia, Pennsylvania.
    \item[3/2021] \textbf{Smith, J. E.}, Davis, C. D., Wilson, E. F. Predictors of Major Adverse Cardiovascular Events
    in Patients with Coronary Microvascular Dysfunction.
    American College of Cardiology Annual Scientific Session,
    Atlanta, Georgia.
    \item[5/2023] \textbf{Smith, J. E.}, Johnson, A. B., Lee, R. S. Impact of Frailty on Outcomes After
    Transcatheter Aortic Valve Replacement: A Multi-Center Analysis.
    Society for Cardiovascular Angiography and Interventions Scientific Sessions, Phoenix, Arizona.
\presentationlistend

\end{document}